Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-15 paper/ms.tex
added planet constraint discussion and some minor edits throughout the paper

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips can happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
CQVs are probably all explained by the same phenomenon, we
therefore discard the ``spot-only'' scenario.

@@

In this work, we aim to find bright and nearby CQVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55; Cycles
1-4).  We present our search methods in Section~\ref{sec:methods}, and
the properties of the resulting CQV catalog in
Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into LP 12-502.  We discuss a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

A point on nomenclature.  CQVs have been called ``transient flux
dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses, and which show large-amplitude variability
linked to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a few
similarities between CQVs and dippers do exist (see
Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
phenomenology and stellar properties are quite different.  At the
risk of introducing yet another standard, we hope to use a
nomenclature that reflects how, when observed over timescales of more
than tens of cycles, CQVs are almost but not exactly periodic.  They
are quasiperiodic.  While the three-type classification scheme
proposed by \citet{2017AJ....153..152S} may indeed provide some
helpful visual distinctions amongst the CQVs, it seems likely that
they are all explained by a single underlying phenomenon, and so we
opt to refer to them by a single empirically descriptive name.  We
also considered names that focused on the presence of transient
corotating clumps, or more generally on circumstellar plasma tori;
for the time being, ``CQV'' seems to more accurately mirror the state
of our ignorance.

@@

We analyzed the ``short'' 120-second cadence data acquired by TESS
between July~2018 and Sep~2022 (Sectors 1-55).  Specifically, we used
the 120-second cadence light curves produced by the Science Processing
and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
the TESS data products from these sectors also included full frame
images with cadences of 600 and 1800 seconds, we limited our scope in
this study for the sake of simplicity in data handling.  In exchange,
we sacrificed both completeness and homogeneity of the selection
function.  While TESS cumulatively observed $\approx$90\% of the sky
for at least one lunar month between July~2018 and Sep~2022, the
120-second cadence data were collected for only a subset of observable
stars during this time due to telemetric constraints
\citep[see][]{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

For our dip-counting pipeline, we began with the PDC\_SAP flux for
each sector, removed non-zero quality flags, and normalized the light
curve to one by dividing out its median value.  We then flattened the
light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
and flattened light curve, we ran a periodogram search, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
below 2 days was identified, we reran the periodogram at a finer grid
to improve the accuracy of the period determination.

Once a star's period $P$ was identified, we binned the phased light
curve to 100 points per cycle.  To separate ``sharp'' local minima
from smooth spot-induced variability, we then iteratively fit robust
penalized splines to the wrapped phase-folded light curve, excluding
points more than two standard deviations away from the local continuum
\citep{2019AJ....158..143H}.  The maximum number of equidistant spline
knots per cycle is the parameter in this framework that controlled the
meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
though for most stars fewer knots were preferred based on
cross-validation using an $\ell^2$-norm penalty.  An example fit is
shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the PDC\_SAP light curves, we normalized each light curve, and then
re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the corrected, padded light curve using {\tt
numpy.fft.fft}, we then searched for peaks with a significance of over
12-$\sigma$ within a set of 500 bins. 
{\bf LB: by the latter ``bins'', does this mean frequencies?}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
within a kiloparsec from \citet{2022AJ....163..121B}, and also
searched the local volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

We determined the stellar effective temperature and radii by fitting
the broadband spectral energy distributions (SEDs); we then estimated
the masses by interpolating against the sizes, temperatures, and ages
against the PARSEC v1.2S models
\citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE 1-2 passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE 3-4, but due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster, primarily using
BANYAN\,$\Sigma$.\footnote{Two of the
	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
	in Table~\ref{tab:thetable}.
	One membership, of TIC~397791443 in IC\,2602, was made manually
	from a literature search
	\citep[e.g.][]{2020A&A...633A..99C}.}  
The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising, since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, any many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, we were not able to confidently associate either
star with any young groups.  Both do seem to show the CQV signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.

Our search confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
knowledge, TIC~332517282 in AB~Dor was the previous record-holder for
oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
least one unambiguous CQV (EPIC~211070495) and a few other candidates
were also previously known in the Pleiades
\citep{2016AJ....152..114R}.

@@

The upper age limit for CQVs may even pass 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
is based on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades and younger than the 400\,Myr Ursa Major
moving group.  The formal BANYAN-$\Sigma$ membership probability is
however somewhat low, perhaps due to the missing radial velocity.
This could be resolved by acquiring even a
medium-resolution spectrum.  An independent assessment of the group's
kinematics using Gaia data, and its rotation sequence using TESS,
could lend further credence in such an analysis.

@@

Most CQVs in our catalog did not show infrared excesses in the W1-W4
bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both W3 and
W4 at $>$3$\sigma$ above the photospheric prediction).

The two IR excess sources were TIC~193136669 (TWA~34) and TIC~57830249
(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
and have relatively long periods of 38\,hr and 44\,hr respectively.
In our initial labeling, we labeled both as ``ambiguous'' CQVs because
the dips in their light curves did not show the rigid periodicity
typical of CQVs;  their periods were also relatively long.  However,
inspection of further sectors clarified that both sources are dippers
(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
193136669 has a cold molecular disk based on observed 1.3\,mm
continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

We incorporated each of these sources of information into a column in
Table~\ref{tab:thetable} that expresses whether any given source
passed each of the binarity indicators.
We discuss some important--and complicated--aspects of the systems
that seem to be binary in Section~\ref{subsec:discbinary}.

>>>>

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips, however, happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
CQVs are probably all explained by the same phenomenon, we
therefore discard the ``spot-only'' scenario.

@@

In this work, we aim to find bright and nearby CQVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 120-second cadence data
acquired by TESS between 2018 July and 2022 September (Sectors 1-55; Cycles
1-4).  We present our search methods in Section~\ref{sec:methods}, and
the properties of the resulting CQV catalog in
Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into LP 12-502.  We discuss a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

A point on nomenclature.  CQVs have been called ``transient flux
dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P},
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses, and which show large-amplitude variability
linked to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a few
similarities between CQVs and dippers do exist (see
Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
phenomenology and stellar properties are quite different.  At the
risk of introducing yet another standard, we hope to use a
nomenclature that reflects how, when observed over timescales of more
than tens of cycles, CQVs are almost but not exactly periodic.  They
are quasiperiodic.  While the three-type classification scheme
proposed by \citet{2017AJ....153..152S} may indeed provide some
helpful visual distinctions amongst the CQVs, it seems likely that
they are all explained by a single underlying phenomenon, and so we
opt to refer to them by a single empirically descriptive name.  We
also considered names that focused on the presence of transient
corotating clumps, or more generally on circumstellar plasma tori;
for the time being, ``CQV'' is agnostic to the true underlying phenomenon.

@@

To construct our sample, we analyzed the short-cadence data acquired by TESS
between 2018 July and 2022 September (Sectors 1-55).  Specifically, we used
the 120-second cadence light curves produced by the Science Processing
and Operations Center at NASA Ames \citep{2016SPIE.9913E..3EJ}.  While
the TESS data products from these sectors also included full frame
images with cadences of 600 and 1800 seconds, we limited our scope in
this study for the sake of simplicity in data handling and some degree of 
uniformity in the properties of the data itself.  In exchange,
we sacrificed both completeness and homogeneity of the selection
function.  While TESS cumulatively observed $\approx$90\% of the sky
for at least one lunar month between 2018 July and 2022 September, the
120-second cadence data were collected for only a subset of observable
stars during this time due to telemetric constraints
\citep[see][]{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
$\approx$50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves satisfying these four conditions:
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only})\\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})\\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}).
\end{align}
Here, $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ is the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and $d$ a geometric distance defined by inverting the
parallax and ignoring any zero-point correction.  The target sample
therefore includes \nstarssearched\ M dwarfs and late-K dwarfs, down
to $T$$<$16 and out to $d$$<$150\,pc.

@@

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux for
each sector, removed non-zero quality flags, and normalized the light
curve to one by dividing out its median value.  We then flattened the
light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  On the resulting cleaned
and flattened light curve, we ran a periodogram search, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer grid
to improve the accuracy of the period determination.

Once a star's period was identified, we binned the phased light
curve to 100 points per cycle.  To separate ``sharp'' local minima
from smooth spot-induced variability, we then iteratively fit robust
penalized splines to the wrapped phase-folded light curve, excluding
points more than two standard deviations away from the local continuum
\citep{2019AJ....158..143H} {\red (RJ: was this to guard against flares?
might be good to explicitly mention, if so.)}.  The maximum number of equidistant spline
knots per cycle is the parameter in this framework that controlled the
meaning of ``sharp'' --- we allowed at most 10 such knots per cycle,
though for most stars fewer knots were preferred based on
cross-validation using an $\ell^2$-norm penalty.  An example fit is
shown in panel {\it (e)} of Figure~\ref{fig:vet}.

@@

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the {\tt PDC\_SAP} light curves, we normalized each light curve, and then
re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the corrected, padded light curve using {\tt
numpy.fft.fft}, we then searched for peaks with a significance of over
12-$\sigma$ within a set of 500 frequency bins.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			{\red (RJ: Will these be made available on Zenodo, or something with a permanent DOI?)}
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
within 1 kpc from \citet{2022AJ....163..121B}, and also
searched the local volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

We determined the stellar effective temperature and radii by fitting
the broadband spectral energy distributions (SEDs); we then estimated
the masses by interpolating against the sizes, temperatures, and ages
of the PARSEC v1.2S models
\citep{2012MNRAS.427..127B,2014MNRAS.444.2525C}.

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE bands $W3$ and $W4$, but due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster, primarily using
BANYAN\,$\Sigma$.\footnote{Two of the
	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
	in Table~\ref{tab:thetable}.
	One membership, of TIC~397791443 in IC\,2602, was made manually
	from a literature search
	\citep[e.g.][]{2020A&A...633A..99C}.}  
The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, we were not able to confidently associate either
star with any young groups.  Both do seem to show the CQV signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.  {\red (RJ: right now, the current value
is 1, but you say "both", would be good to fix this consistency issue)}

Our search confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three
$\approx$150\,Myr CQVs in AB~Dor \citep{2015MNRAS.454..593B}, a
$\approx$112\,Myr old Pleiades CQV \citep{2015ApJ...813..108D}, and a
similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our
knowledge, TIC~332517282 in AB~Dor was the previous record-holder for the
oldest-known CQV \citep{2019ApJ...876..127Z,2022AJ....163..144G}; at
least one unambiguous CQV (EPIC~211070495) and a few other candidates
were also previously known in the Pleiades
\citep{2016AJ....152..114R}.

@@

The upper age limit for CQVs may even pass 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age
is based on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades but younger than the 400\,Myr Ursa Major
moving group.  The formal BANYAN-$\Sigma$ membership probability is
however somewhat low, perhaps due to the missing radial velocity.
This lack of information could be resolved by acquiring even a
medium-resolution spectrum.  An independent assessment of the group's
kinematics using Gaia data, and its rotation sequence using TESS,
could lend further credence in such an analysis.

@@

Most CQVs in our catalog did not show infrared excesses in the $W1--W4$
bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$ and
$W4$ at $>$3$\sigma$ above the photospheric prediction).

The two sources exhibiting an IR excess were TIC~193136669 (TWA~34) and TIC~57830249
(TWA~33).  Both are in the TW Hydrae association ($\approx$10\,Myr),
and have relatively long periods of 38\,hr and 44\,hr respectively.
In our initial labeling, we labeled both as ``ambiguous'' CQVs because
the dips in their light curves did not show the rigid periodicity
typical of CQVs;  their periods were also relatively long.  However,
inspection of further sectors clarified that both sources are dippers
(see online plots in Figure~\ref{fig:vet}).  Independently, TIC
193136669 has a cold molecular disk based on observed 1.3\,mm
continuum emission and resolved Keplerian $^{12}{\rm CO}(2-1)$
emission \citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

We incorporated each of these sources of information into a column in
Table~\ref{tab:thetable} that expresses whether any given source
passed each of the binarity indicators.
We discuss some important---and complicated---aspects of the systems
that seem to be binary in Section~\ref{subsec:discbinary}.
